Team size and composition in home health care

### 2023-10-25 paper-presentation/paper-presentation.qmd
Added final slide

>>>>

# 'Optimal' team-composition
::: columns
::: {.column width="50%"}
$$\lambda_1\frac{\mathbb{E}[N]}{C}+\lambda_3\mathbb{P}(P \le l)−\lambda_4 ∑_{k∈Q}(\frac{C_k}{∑_{j∈Q}C_j}- \frac{\mu_k}{∑_{j∈Q}\mu_j}) −\lambda_6\frac{M(M−1)}{2}$$
:::

::: {.column width="65%"}
![](images/optimal.png){width="900"}
:::
:::
